Continuous gravitational waves in the lab: recovering audio signals with a table-top~optical microphone

### 2021-08-03 paper/ifo-complexAudio.tex
proof-read after integration of 2nd round of referee comments

We use the Michelson interferometer as an ``optical microphone'', where a laser is used to detect sound instead of the electrical components in a conventional microphone.
The only change to our apparatus is replacing the webcam with a photodiode to allow us to capture higher frequencies neccessary for speech and music (see Section~\ref{sec:photodiode}). 
Optical microphones have precedence in the laser microphones~\cite{laser_microphone} which are (or were historically) used in the defense industry and operate on a variety of related principles. 
%We use the term ``optical microphone'' to distinguish this technology from those previous technologies.
Our objective is to play a recording of speech or music through the speaker attached to mirror M2 (see Fig.~\ref{fig:ifo_schematic_webcam}), record the resulting interference pattern, and then recover the original signal via a selection of signal processing techniques.

This analysis is indirectly related to the advanced signal processing techniques required to extract gravitational-wave signals. 
In addition, the apparatus serves as an independent demonstration for a broader physics and engineering audience, particularly in undergraduate laboratories. 
We describe additional hardware components required for this demonstration in Section~\ref{sec:photodiode} and the initial results in Section~\ref{sec:initialResultsOpMic}. 
We consider a selection of filter techniques, details of which can be found in the Supplementary Material, where we also refer the reader to a selection of digital signal processing resources for further information. 
In Section~\ref{sec:opticalMicResults}, we present the two best-performing analyses from our Supplementary Material.

\subsection{Hardware modifications for the optical microphone}
\label{sec:photodiode}
The human ear can hear frequencies in the range of $\sim 20\,{\rm Hz}$--$20\,{\rm kHz}$. 
Speech intelligibility (being able to understand speech) requires frequencies up to $3\,{\rm kHz}$ and music requires up to and beyond $8\,{\rm kHz}$. 
Therefore, the optical microphone requires a sample rate of at least $16\,{\rm kHz}$ to capture both speech and music (adjusting for the Nyquist frequency). 
This cannot be achieved with the webcam used in Sections~\ref{sec:single_tone} and ~\ref{sec:viterbi_wandering} as it has a sampling rate of $30\,{\rm Hz}$ and thus can only ``hear'' frequencies below $15\,{\rm Hz}$.
To overcome this issue, we use a photodiode~\footnote{A photodiode is an electrical component that acts as a regular diode when no light is incident on it, blocking any current flow in the reverse direction. As the intensity of incident light rises, it becomes increasingly conductive in the reverse direction.} at the output of the interferometer to achieve a sampling rate of $16\,{\rm kHz}$.

We place an OSRAM BPW21 photodiode in reverse-bias over an LM358 op-amp which together produce a voltage that depends on the incident intensity. 
The photodiode records the interference pattern at roughly the same off-center position as the webcam in Sections~\ref{sec:single_tone} and~\ref{sec:viterbi_wandering}, again chosen arbitrarily.
% I think this is probably not needed as I believe the editor comment is referring to the cloth screen over the photodiode, which is addressed below. 
%The photodiode is mounted on a piece of cloth stretched over a plastic frame, with the electrical leads connected underneath the cloth.
%This cloth screen mount was the ``grill cloth'' from the front of a dismantled commercial speaker, re-purposed. 
The voltage signal from the photo-detector is captured by an MCP3008 $10$-bit analog-to-digital converter (ADC) connected to a Raspberry Pi Model 3 v1.2 (henceforth: Pi), which provides a convenient means to record the photodiode data.
Together, the circuit samples the signal at $\sim 16\,{\rm kHz}$. 
Resources for using the Pi and photodiode, including a circuit diagram, are described the Supplementary Material.

@@

The raw output of the optical microphone (with anti-aliasing) is noisy with a loud bass continuous hum. 
This can be explained by looking at the power spectral density (PSD) of the background noise (i.e., with the speaker switched off), shown in Fig.~\ref{fig:psd_noise}. 
The spectrum is dominated by AC mains noise with power from the fundamental $50\,{\rm Hz}$ Australian mains power grid signal up to and beyond $8$th harmonic. 
The mains signal is also present, but far weaker, in the background spectrum taken with the photodiode in darkness, suggesting that ambient lighting has a large contribution. 
Besides lighting, other possible contributions to the mains signal include air conditioning and the photodiode circuit itself. 
The appearance of harmonics of the mains noise is likely due to non-linearity in the system. 
The spectrum in Fig.~\ref{fig:psd_noise} also has a broad feature at around $750\,{\rm Hz}$, the origin of which is yet to be determined.
Environmental noise reduction for gravitational-wave detectors is an active area of research (see the accompanying Supplementary Material for further information and resources on this topic).

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/combined_highlight_results_melatos_labelled.pdf}
\caption{\label{fig:notchWienerLogMMSEResults}
Timeseries (left column) and frequency spectrum (right column) results with the optical microphone. 
The original input signal in the first row is a $1\,{\rm s}$ recording of an adult male voice (saying ``A cathode''). 
 The input signal is shifted by 0.12 s to the right to synchronize the manual delay from starting the recording with the Raspberry Pi and starting to play the source through the speaker. 
The second row shows the raw output from the optical microphone when the input from the first row is played. 
The third row shows the result of applying the notch and Wiener filter combined. 
The fourth row shows the result of applying the logMMSE estimator, where the rise at the start of the timeseries is an expected effect when filtering a signal of finite duration. 
}
\end{center}
\end{figure*}

We explore several filters to remove the $50\,{\rm Hz}$ mains hum and harmonics, and also to improve the speech intelligibility of the recording.
The accompanying Supplementary Material describes a range of analysis techniques that can be used as examples for the undergraduate laboratory. 
All filters are tested on the same $1\,{\rm s}$ long speech recording.
The results of this section are shown in Fig.~\ref{fig:notchWienerLogMMSEResults}. 
In the figure the left and right columns show the timeseries and frequency spectrum respectively. 
The first row shows the input signal played through the speaker (see Fig.~\ref{fig:ifo_schematic_webcam}). 
The second row shows the raw output from the photodiode recording.

@@

In this section, we present the results of two advanced signal processing analysis techniques applied to the optical microphone recordings. 
The techniques are only briefly described here and we refer the reader to the accompanying Supplementary Material for further details and other analysis techniques.

Firstly, we consider two signal processing techniques used in combination: the cascaded notch and the Wiener filter (see also the Supplementary Material). 
A notch filter removes signals within a specific frequency range. 
We want to remove the $50\,{\rm Hz}$ mains noise and harmonics, therefore we use a cascaded notch filter where each notch is centered at each of the harmonics. 
The Wiener filter is an advanced statistical technique that makes use of statistical information from the speech data and noise. 
It amplifies parts of the signal with high signal-to-noise (SNR) ratio while suppressing parts with low SNR. 
The results of the combined cascaded notch and Wiener filter are shown in the third row in Fig.~\ref{fig:notchWienerLogMMSEResults}. 
Most of the mains noise is removed, however the recovered voice sounds muffled and is not understandable.

Secondly, we apply a speech enhancement technique. 
Ref.~\cite{SubjectiveComparison} compares $13$ speech enhancement methods, finding the log minimum mean-square error (logMMSE) estimator to be the best, qualitatively, at recovering speech (see also the Supplementary Material). 
We use an existing implementation of the logMMSE from~\cite{logmmse}.  
The logMMSE estimator results are shown in the bottom panels in Fig.~\ref{fig:notchWienerLogMMSEResults}. 
We see significant attenuation of the mains harmonics and general smoothing of the spectrum. 
Most of the background noise is removed, however, the logMMSE does not significantly enhance the speech as the voice sounds muffled and indistinct.

We find some improvement with music over speech. 
Simple chords and drums can be heard, however more composite sounds and complex melodies cannot be heard clearly. 
Our observations suggest that this is especially true for certain instruments; in particular flutes and violins sometimes can’t be heard at all. 
This could be a perceptual effect or a frequency dependence somewhere in the optical microphone.
Speculating, perhaps the speaker-mirror coupling is stronger at low frequencies and thus instruments like electric bass and drums are louder in the results.
To address these problems, we need to determine whether the signals that are audibly missing (the diction in the speech and complex melodies in music) are indeed being transmitted through the optical microphone at all. 
To determine this requires a better understanding of the system, as discussed in Section~\ref{sec:future_work}.

>>>>

We use the Michelson interferometer as an ``optical microphone'', where a laser is used to detect sound instead of the electrical components in a conventional microphone.
The only change to our apparatus is replacing the webcam with a photodiode to allow us to capture higher frequencies necessary for speech and music (see Section~\ref{sec:photodiode}). 
Optical microphones have precedence in the laser microphones~\cite{laser_microphone} which are (or were historically) used in the defense industry and operate on a variety of related principles. 
%We use the term ``optical microphone'' to distinguish this technology from those previous technologies.
Our objective is to play a recording of speech or music through the speaker attached to mirror M2 (see Fig.~\ref{fig:ifo_schematic_webcam}), record the resulting interference pattern, and then recover the original signal via a selection of signal processing techniques.

This analysis is indirectly related to the advanced signal processing techniques required to extract gravitational-wave signals. % citation?
In addition, the apparatus serves as an independent demonstration for a broader physics and engineering audience, particularly in undergraduate laboratories. 
We describe additional hardware components required for this demonstration in Section~\ref{sec:photodiode} and the initial results in Section~\ref{sec:initialResultsOpMic}. 
We consider a selection of filter techniques, details of which along with a summary of digital signal processing resources can be found in the Supplementary Material.
 % We also refer the reader to a selection of digital signal processing resources for further information. 
In Section~\ref{sec:opticalMicResults}, we present the two best-performing techniques from the Supplementary Material.

\subsection{Hardware modifications for the optical microphone}
\label{sec:photodiode}
The human ear can hear frequencies in the range of $\sim 20\,{\rm Hz}$--$20\,{\rm kHz}$. 
Speech intelligibility (the ability to understand speech) requires frequencies up to $3\,{\rm kHz}$ and music requires up to and beyond $8\,{\rm kHz}$. 
Therefore, the optical microphone requires a sample rate of at least $16\,{\rm kHz}$ to capture both speech and music (adjusting for the Nyquist frequency). 
This cannot be achieved with the webcam used in Sections~\ref{sec:single_tone} and ~\ref{sec:viterbi_wandering} as it has a sampling rate of $30\,{\rm Hz}$ and thus can only ``hear'' frequencies below $15\,{\rm Hz}$.
To overcome this issue, we use a photodiode~\footnote{A photodiode is an electrical component that acts as a regular diode when no light is incident on it, blocking any current flow in the reverse direction. As the intensity of incident light rises, it becomes increasingly conductive in the reverse direction.} at the output of the interferometer to achieve a sampling rate of $16\,{\rm kHz}$.

We place an OSRAM BPW21 photodiode in reverse-bias over an LM358 op-amp which together produce a voltage that depends on the incident intensity. 
The photodiode records the interference pattern at roughly the same off-center position as the webcam in Sections~\ref{sec:single_tone} and~\ref{sec:viterbi_wandering}, again chosen arbitrarily.
% I think this is probably not needed as I believe the editor comment is referring to the cloth screen over the photodiode, which is addressed below. 
%The photodiode is mounted on a piece of cloth stretched over a plastic frame, with the electrical leads connected underneath the cloth.
%This cloth screen mount was the ``grill cloth'' from the front of a dismantled commercial speaker, re-purposed. 
The voltage signal from the photo-detector is captured by an MCP3008 $10$-bit analog-to-digital converter (ADC) connected to a Raspberry Pi Model 3 v1.2, which provides a convenient means to record the photodiode data.
Together, the circuit samples the signal at $\sim 16\,{\rm kHz}$. 
Resources for using the Raspberry~Pi and photodiode, including a circuit diagram, are described in the Supplementary Material.

@@

The raw output of the optical microphone (with anti-aliasing) is noisy with a loud, continuous bass hum. 
This can be explained by looking at the power spectral density (PSD) of the background noise (i.e., the output with the speaker switched off), shown in Fig.~\ref{fig:psd_noise}. 
The spectrum is dominated by AC mains noise with power from the fundamental $50\,{\rm Hz}$ Australian mains power grid signal up to and beyond $8$th harmonic. 
The mains signal is also present, but far weaker, in the background spectrum taken with the photodiode in darkness, suggesting that ambient lighting has a large contribution. 
Besides lighting, other possible contributions to the mains signal include air conditioning and the photodiode circuit itself. 
The appearance of harmonics of the mains noise might be due to the non-linearity in the system discussed in Section~\ref{sec:ifo}. 
The spectrum in Fig.~\ref{fig:psd_noise} also has a broad feature at around $750\,{\rm Hz}$, the origin of which is yet to be determined.
Environmental noise reduction for gravitational-wave detectors is an active area of research (see the Supplementary Material for further information and resources on this topic).

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/combined_highlight_results_melatos_labelled.pdf}
\caption{\label{fig:notchWienerLogMMSEResults}
Timeseries (left column) and frequency spectrum (right column) results with the optical microphone. 
The original input signal in the first row is a $1\,{\rm s}$ recording of an adult male voice (saying ``a cathode''). 
 The input signal is shifted by 0.12 s to the right to synchronize the manual delay from starting the recording with the Raspberry Pi and starting to play the source through the speaker. 
The second row shows the raw output from the optical microphone when the input from the first row is played. 
The third row shows the result of applying the notch and Wiener filters combined. 
The fourth row shows the result of applying the logMMSE estimator, where the rise at the start of the timeseries is an expected effect when filtering a signal of finite duration. 
}
\end{center}
\end{figure*}

We explore several filters to remove the $50\,{\rm Hz}$ mains hum and harmonics and improve the speech intelligibility of the recording.
The Supplementary Material describes a range of analysis techniques that can be used as examples for the undergraduate laboratory. 
All filters are tested on the same $1\,{\rm s}$ long speech recording.
The results of this section are shown in Fig.~\ref{fig:notchWienerLogMMSEResults}. 
In the figure, the left and right columns show the timeseries and frequency spectrum respectively. 
The first row shows the input signal played through the speaker (see Fig.~\ref{fig:ifo_schematic_webcam}). 
The second row shows the raw output from the photodiode recording.

@@

In this section, we present the results of two advanced signal processing analysis techniques applied to the optical microphone recordings. 
The techniques are only briefly described here and we refer the reader to the Supplementary Material for further details and other analysis techniques.

Firstly, we consider two signal processing techniques used in combination: the cascaded notch and the Wiener filter (see also the Supplementary Material). 
A notch filter removes signals within a specific frequency range. 
We want to remove the $50\,{\rm Hz}$ mains noise and harmonics, therefore we use a cascaded notch filter where each notch is centered at each of the harmonics. 
The Wiener filter is an advanced statistical technique that makes use of statistical information from the speech data and noise. 
It amplifies parts of the signal with high signal-to-noise ratio while suppressing parts with low signal-to-noise ratio. 
The results of the combined cascaded notch and Wiener filter are shown in the third row in Fig.~\ref{fig:notchWienerLogMMSEResults}. 
Most of the mains noise is removed, however, the recovered voice sounds muffled and is not understandable.

Secondly, we apply a speech enhancement technique. 
Ref.~\cite{SubjectiveComparison} compares $13$ speech enhancement methods, finding the log minimum mean-square error (logMMSE) estimator to be the best, qualitatively, at recovering speech (see also the Supplementary Material). 
We use an existing implementation of the logMMSE from Ref.~\cite{logmmse}.  
The logMMSE estimator results are shown in the bottom panels in Fig.~\ref{fig:notchWienerLogMMSEResults}. 
We see significant attenuation of the mains harmonics and general smoothing of the spectrum. 
Most of the background noise is removed, however, the logMMSE still does not significantly enhance the speech as the voice sounds muffled and indistinct.

We find some improvement with music over speech. 
Simple chords and drums can be heard after filtering, however, more composite sounds and complex melodies cannot be heard clearly. 
Our observations suggest that this is especially true for certain instruments; in particular flutes and violins sometimes can’t be heard at all. 
This could be a perceptual effect or a frequency dependence somewhere in the optical microphone.
Speculating, perhaps the speaker-mirror coupling is stronger at low frequencies and thus instruments like electric bass and drums are louder in the results.
To address these problems, we need to determine whether the signals that are audibly missing (the diction in the speech and complex melodies in music) are indeed being transmitted through the optical microphone at all. 
To determine this requires a better understanding of the system, as discussed in Section~\ref{sec:future_work}.

### 2021-08-03 paper/ifo-conclusions.tex
proof-read after integration of 2nd round of referee comments

In this paper, we use a table-top Michelson interferometer as an analog to a gravitational-wave detector, demonstrating signal processing techniques used within the gravitational-wave community.
We explore the use of the interferometer as an optical microphone, considering a more general treatment of signal processing with complex audio signals, which can also serve as a more distant analog to un-modeled gravitational-wave burst signals, e.g., from supernova.
The demonstration can be adapted for use in the undergraduate laboratory and as an tool for explaining gravitational-wave research to a wider, non-specialist audience.

>>>>

In this paper, we use a table-top Michelson interferometer as an analog to a gravitational-wave detector, demonstrating signal processing techniques used within the gravitational-wave community.
We explore the use of the interferometer as an optical microphone and consider a more general treatment of signal processing with complex audio signals, which can also serve as a distant analog to un-modeled gravitational-wave burst signals, e.g., from supernovae.
% justify ``un-modeled''? - james
The demonstration can be adapted for use in the undergraduate laboratory and as a tool for explaining gravitational-wave research to a wider, non-specialist audience.

### 2021-08-03 paper/ifo-futureWork.tex
proof-read after integration of 2nd round of referee comments

\begin{figure*}
    \includegraphics[width=.8\textwidth]{figures/pipeline_nobox.pdf}
	%\includegraphics[height=.8\textwidth, angle=-90]{figures/pipeline.pdf}
	\caption{\label{fig:pipeline_highlighted}
Flowchart for the signal through the optical microphone. 
A transfer function of the system would have to account for each stage and an aim of future work. 
Not shown are the signal processing filters that are performed on the PC once the data is transferred off the Pi.
}
\end{figure*}

@@

Isolating the experiment from interference may provide some noise reduction. 
The Raspberry Pi could be powered with a commercial battery instead of mains power, which may help to isolate the circuit from the mains as all other components draw power from the Pi (the laser is DC-powered through a converter).
Transferring the circuit from a breadboard to a printed circuit board can also reduce interference~\cite{elfekey2013design}.
A feedback loop control system can also be used to suppress any unwanted movement of the interferometer components~\citep{abbott2017exploring, Sekiguchi:2016bmv, verhoeven2009robust}, similar to methods used to isolate gravitational-wave observatories.

A thorough characterization of the system's transfer function would allow us to understand how audio signals couple through the interferometer. 
The total transfer function starts with the voltage being sent to the speaker and ends with the voltage recorded by the Pi. 
It would include any inherent non-linearities in the speaker, the speaker-mirror coupling, the path length to intensity relation, and the photodiode. 
The schematic in Fig.~\ref{fig:pipeline_highlighted} shows the abstract signal flow through the system.
It does not include other potential pathways for signal flow such as acoustomechanical vibrations of the webcam or photodiode mount which could also be examined.

@@

More traditional techniques such as a wavelet transform (WT)~\citep{nason1995stationary} could be used to extract the signal from noise, and compared with the above methods. 
A WT provides both time and frequency information, making it easier to pinpoint the origin of noise with respect to time. 
In Refs.~\cite{tufekci2000feature,agbinya1996discrete}, WT methods are proposed for speech recognition.

Returning to the demonstration of gravitational wave analysis, single interferometers cannot detect directional information for signals; a large proportion of the directional information in gravitational-wave detections comes from the time delay offset between the signal being recorded at two or more detectors~\cite{GW150914}.
We could therefore extend this analysis to include data from two interferometers to extract directional information.
This would require increasing the sensitivity of the optical microphone to pick up the signal from a distant source instead of from a speaker attached directly to one of the mirrors of the interferometer.
Another extension would be to demonstrate the Doppler effect of the Earth's motion around the Sun, which needs to be considered in continuous-wave searches (see Section~\ref{sec:realCWSearches} and Ref.~\cite{JKS:1998}). 
One approach could be to modify the input audio signal to simulate Doppler modulation.

>>>>

\begin{figure*}
    \includegraphics[width=.8\textwidth]{figures/pipeline_nobox.pdf}
	%\includegraphics[height=.8\textwidth, angle=-90]{figures/pipeline.pdf}
	\caption{\label{fig:pipeline_highlighted}
Flowchart for the signal through the optical microphone. 
A transfer function of the system would have to account for each stage and is an aim of future work. 
Not shown are the signal processing filters that are performed on the PC once the data is transferred off the Raspberry~Pi.
}
\end{figure*}

@@

Isolating the experiment from interference may provide some noise reduction. 
The Raspberry Pi could be powered with a commercial battery instead of mains power, which may help to isolate the circuit from the mains as all other components draw power from the Raspberry~Pi (the laser is DC-powered through a converter).
Transferring the circuit from a breadboard to a printed circuit board can also reduce interference~\cite{elfekey2013design}.
A feedback loop control system can also be used to suppress any unwanted movement of the interferometer components~\citep{abbott2017exploring, Sekiguchi:2016bmv, verhoeven2009robust}, similar to methods used to isolate gravitational-wave observatories.

A thorough characterization of the system's transfer function would allow us to understand how audio signals couple through the interferometer. 
The total transfer function starts with the voltage being sent to the speaker and ends with the voltage recorded by the Raspberry~Pi. 
It would include any inherent non-linearities in the speaker, the speaker-mirror coupling, the path length to intensity relation, and the photodiode. 
The schematic in Fig.~\ref{fig:pipeline_highlighted} shows the abstract signal flow through the system.
It does not include other potential pathways for signal flow such as acoustomechanical vibrations of the webcam or photodiode mount which could also be examined.

@@

More traditional techniques such as a wavelet transform~\citep{nason1995stationary} could be used to extract the signal from noise, and compared with the above methods. 
A wavelet transform provides both time and frequency information, making it easier to pinpoint the origin of noise with respect to time. 
In Refs.~\cite{tufekci2000feature,agbinya1996discrete}, wavelet transform methods are proposed for speech recognition.

Returning to the demonstration of gravitational wave analysis, single interferometers cannot detect directional information for signals; a large proportion of the directional information in gravitational-wave detections comes from the time delay offset between the signal being recorded at two or more detectors~\cite{GW150914}.
We could therefore extend this analysis to include data from two interferometers to extract directional information.
This would require increasing the sensitivity of the optical microphone to pick up the signal from a distant source instead of from a speaker attached directly to one of the mirrors of the interferometer.
Another extension would be to demonstrate the Doppler effect of the Earth's motion around the Sun, which needs to be considered in continuous-wave searches (see Section~\ref{sec:realCWSearches} and Ref.~\cite{JKS:1998}). 
One approach could be to modify the input audio signal to simulate Doppler modulation. 
% did we cut the turn-table idea? that was fun! - james

### 2021-08-03 paper/ifo-singleTone.tex
proof reading, minor typo fixes and edit
proof-read after integration of 2nd round of referee comments

\begin{figure}
	\includegraphics[width=.5\textwidth]{figures/webcam_spectrum_expt_4_0209.pdf}
	\caption{\label{fig:webcam_spectrum}
Recovery of a tone at a constant frequency: Here, we plot the Fourier amplitude of the intensity pattern against frequency.
The injected signal has a frequency of $2.09\,{\rm Hz}$, while the recovered signal peaks at $2.099\,{\rm Hz}$ and has an FWHM of $0.033\,{\rm Hz}$.
The plot also shows two harmonics at $4.19\,{\rm Hz}$ and $6.28\,{\rm Hz}$ with amplitudes $10.3 \%$ and $9.8 \%$ of the amplitude of the primary peak, respectively.
}	
\end{figure}

% rearranged as I found this section to not switch between method and results too much, I've tried this order now: intro, webcam and data specifics, injection, and results. 
Continuous-wave searches look for nearly monochromatic signals~\cite{JKS:1998}. In this section, we consider a simple sinusoidal tone at a single, constant frequency. %should be a single constant frequency *signal*?

@@

%The intensity of the interference pattern is measured at a single point on the screen using a commercial USB webcam (see Fig.~\ref{fig:ifo_schematic_webcam}). The webcam samples at a rate of $30\,{\rm Hz}$, which limits the spectral content of observable signals to below $15\,{\rm Hz}$, the Nyquist frequency. A tone with a frequency of $2.09\,{\rm Hz$} is played through the speaker for one minute and the interference pattern is recorded by the webcam.

A tone with a frequency of $2.09\,{\rm Hz}$ is played through the speaker for one minute. 
The amplitude of the Fourier transform of the recovered signal is shown in Fig.~\ref{fig:webcam_spectrum}. The Discrete Fourier transform was calculated using the NumPy package for Python (see Appendix~\ref{app:code}).
% moved refs~\cite{numpy}~\footnote{\url{https://numpy.org/doc/stable/reference/routines.fft.html}}.
We measured a peak amplitude at $2.099\,{\rm Hz}$ with a full width half maximum (FWHM) of $0.033\,{\rm Hz}$.
Two harmonics can also be seen at integer multiples of the peak frequency. 
The peaks at $4.19\,{\rm Hz}$ and $6.28\,{\rm Hz}$ have amplitudes of $0.103$ and $0.098$ as a fraction of the height of the main peak, respectively. They are likely due to the nonlinear response of the system discussed in Section~\ref{sec:ifo}.
Also, note that the noise appears to rise at lower frequencies.

>>>>

\begin{figure}
	\includegraphics[width=.5\textwidth]{figures/webcam_spectrum_expt_4_0209.pdf}
	\caption{\label{fig:webcam_spectrum}
Recovery of a tone at a constant frequency: the Fourier amplitude of the intensity pattern against frequency.
The injected signal has a frequency of $2.09\,{\rm Hz}$, while the recovered signal peaks at $2.099\,{\rm Hz}$ and has an FWHM of $0.033\,{\rm Hz}$.
The plot also shows two harmonics at $4.19\,{\rm Hz}$ and $6.28\,{\rm Hz}$ with amplitudes $10.3 \%$ and $9.8 \%$ of the amplitude of the primary peak, respectively.
}	
\end{figure}

Continuous-wave searches look for nearly monochromatic signals~\cite{JKS:1998}. In this section, we consider a simple sinusoidal tone at a single, constant frequency.

@@

A tone with a frequency of $2.09\,{\rm Hz}$ is played through the speaker for one minute. 
The amplitude of the Fourier transform of the recovered signal is shown in Fig.~\ref{fig:webcam_spectrum}. The Discrete Fourier transform is calculated using the NumPy package for Python (see Appendix~\ref{app:code}).
We measured a peak amplitude at $2.099\,{\rm Hz}$ with a full width half maximum (FWHM) of $0.033\,{\rm Hz}$.
Two harmonics can also be seen at integer multiples of the peak frequency. 
The peaks at $4.19\,{\rm Hz}$ and $6.28\,{\rm Hz}$ have amplitudes of $0.103$ and $0.098$ as a fraction of the height of the main peak, respectively. They are likely due to the nonlinear response of the system discussed in Section~\ref{sec:ifo}.
Also, note that the noise appears to rise at lower frequencies.
